%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\usepackage[margin=0.35in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
     
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\eduSubheading}[7]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \vspace{-2pt}
      \textit{\small#3} & \hspace{-10cm}\textit{\small #4} \\
      \vspace{-2pt}
      \textit{\footnotesize#5}&\textit{\small #6} \\
      
      \textit{\footnotesize#7}
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
\textbf{\Huge \scshape Yicheng (Dennis) Wang} \\ \vspace{1pt}
\small Boston, MA  $|$ Available July - December 2025 $|$ \href{mailto:denniswang812@gmail.com}{\underline{denniswang812@gmail.com}} $|$ (949) 375-1978 $|$ \href{https://www.linkedin.com/in/denniswang812/}{\underline{Linkedin}} $|$ \href{https://github.com/denniwang}{\underline{Github}} 
\end{center} 


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \eduSubheading
      {Northeastern University - Khoury College of Computer Science}{Boston, MA}
      {Candidate for a Bachelor of Science in Computer Science + Business} {Sep. 2023 -- Present}
       {Courses: Object-Oriented Design, Programming Languages, Data Structures + Algorithms, Profit Analysis}{Expected: May 2026}
       {Honors: Dean's List; GPA: 3.81/4.00;}
  \resumeSubHeadingListEnd


%----------- SKILLS-----------
\section{Technical Skills \& Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Frameworks}{: React, Nextjs, TypeScript, Java, Python, Tailwind CSS, Chakra UI, Express, Node.js, Flask} \\
     \textbf{Developer Tools}{: VSCode, Git, Postman, npm, Netlify, Vercel, Supabase, MongoDB, Docker,  Amazon Web Services} \\
     \textbf{Interests}{: Tennis, cooking, nonprofit work, college consulting, skiing, running, hiking, real estate, hackathons, traveling}
     \vspace{-5pt}
    }}
    
 \end{itemize}

%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart
      \vspace{2pt}
   \resumeSubheading
      {Software Engineer}{Sep. 2024 - Present}
      {Digital Archive of Indigenous Language Persistence (DAILP)}{Northeastern Digital Scholarship Group, Boston, MA}
      \resumeItemListStart
        \resumeItem{Integrating glossary translation support for Cherokee words, potentially benefiting over 2,000 fluent speakers and 10,000-20,000 language learners.}
        \resumeItem{Engineering key features for DAILP's web dictionary application, enhancing Cherokee language preservation and cultural heritage documentation efforts.}
        \resumeItem{Practicing effective communication and teamwork in weekly check-in meetings with technical lead and other developers.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd



   
\section{Leadership Experience}
  \resumeSubHeadingListStart
    \vspace{2pt}
     \resumeSubheading
      {Head of Developer Experience + Developer}{Sep. 2024 - Present}
      {Sandbox}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Increased new developer productivity by 65\% with 3 onboarding workshops about React, GitHub, and Postman.}
        \resumeItem{Teaching beginner web developers React on project team during pair-progamming sessions to improve team efficiency.}
        \resumeItem{Participating in sprints and weekly stand-ups in an Agile development environment to ensure effective project delivery.}
        
    \resumeItemListEnd
   \resumeSubheading
      {Technical Mentor}{Sep. 2024 - Dec. 2024}
      {Oasis}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Mentored 8 beginner developers in 25+ hack sessions, maintaining a 100\% developer-retention rate.}
        \resumeItem{Guided project planning, design, and implementation with strong time-management and organizational skills.}
        \resumeItem{Simplified web development concepts and addressed questions promptly when leading workshops for new developers.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd





%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
             \resumeProjectHeading
          {\textbf{GraduateNU} $|$ \emph{Northeastern degree audit website: React, Nestjs}}{Sep. 2024 - Present}
          \resumeItemListStart
            \resumeItem{Developing degree audit platform empowering 15,000+ Northeastern undergraduates with fast and reliable academic planning.}
            \resumeItem{Expanded app to support 468 academic minors, allowing seamless integration of minor requirements into degree plans.}
            \resumeItem{Leveraged browser-based storage sandbox area to empower students with on-site note-taking for improved planning.} 
            \resumeItem{Implemented a cross-project API function to fetch information about individual courses in a degree audit plan.}
          \resumeItemListEnd

       \resumeProjectHeading
          {\textbf{Securing Safe Food} $|$ \emph{Nonprofit pantry managment dashboard: React, Nestjs}}{Sep. 2024 - Jan. 2025}
            \resumeItemListStart
            \resumeItem{Launched pantry management interface for Securing Safe Food, a 501(c)(3) nonprofit providing 30+ pantries with allergen-friendly food.}
            \resumeItem{Developed essential CRUD API endpoints for admins, including robust authentication to protect sensitive data.}
            \resumeItem{Designed intuitive React components for user authentication, prioritizing accessibility for users of all backgrounds.}
          \resumeItemListEnd
          
       \resumeProjectHeading
          {\textbf{T-Error} $|$ \emph{Terminal error tracker: C++, Nextjs, Express.js}}{Oct. 2024}
          \resumeItemListStart
            \resumeItem{Centralized platform for terminal error tracking, winning "Best Developer Tool" at HackHarvard 2024.}
            \resumeItem{Designed Nextjs dashboard with language processing to classify 100+ errors captured by custom C++ shell wrapper.}
            \resumeItem{Orchestrated efficient team collaboration and project management, minimizing merge conflicts to 5 across 99 commits.}
          \resumeItemListEnd
          
     \resumeProjectHeading
        {\textbf{EquilibriNews} $|$ \emph{Nextjs, Playwright, Puppeteer}}{Apr. 2022 - Jan. 2024}
        \resumeItemListStart
            \resumeItem{Deployed a news application that aggregates and presents news from 8 major publishers, reducing political bias through balanced content presentation.}
            \resumeItem{Leveraged Playwright and Google's Puppeteer API to efficiently scrape data from diverse news website, including The New York Times, Fox News, and The Wall Street Journal.}
            \resumeItem{Optimized web scraping algorithms, resulting in 30\% reduction in data retrieval time and improved overall performance.}
          \resumeItemListEnd
          \resumeItemListEnd 
%-------------------------------------------
\end{document}
