%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
     
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\eduSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5}
     
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
\textbf{\Huge \scshape Yicheng (Dennis) Wang} \\ \vspace{1pt}
\small 949-375-1978 $|$ \href{mailto:denniswang812@gmail.com}{\underline{denniswang812@gmail.com}} $|$ \href{https://www.linkedin.com/in/denniswang812/}{\underline{LinkedIn}} $|$ \href{https://github.com/hellolol2016}{\underline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \eduSubheading
      {Northeastern University}{Boston, MA}
      {Bachelor of Science in Computer Science + Business Administration; GPA: 3.88} {Sep. 2023 -- May. 2027}
        {Relevant Courses: Fundamentals of CS 1+2 (A), Object-Oriented Design (IP)}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}

%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Software Engineer}{Sep. 2024 - Present}
      {Sandbox}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Participated in sprints and weekly stand-ups in an Agile development environment to ensure efficient project delivery}
        \resumeItem{Performing bi-weekly PR reviews and practicing pair-programming to tackle 3 high-priority tickets per month.}
       \resumeItem{Implementing features in a degree audit application impacting 15,000+ undergraduate students' academic planning process}
        
    \resumeItemListEnd

       \resumeSubheading
      {Developer}{Sep. 2024 - Present}
      {Code 4 Community}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Creating solutions for Securing Safe Food, a 501(c)(3) nonprofit empowering 30+ pantries with allergen-friendly food.}
        \resumeItem{Engaging in weekly meetings and code reviews for an inventory and delivery management platform for pantries.}
        \resumeItem{Developing fundamental backend functions, ensuring user authentication when manipulating potentially sensitive data.}
    \resumeItemListEnd

   \resumeSubheading
      {Mentor}{Sep. 2024 - Present}
      {Oasis}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Mentoring 8 rookie developers in 25+ hack sessions outside of club hours, maintaining a 100\% developer-retention rate}
        \resumeItem{Guiding project planning, tech stack selection, and development with strong time-management and organizational skills.}
        \resumeItem{Simplified web-dev concepts and addressed questions promptly when leading workshops for new developers.}
    \resumeItemListEnd
  
 \resumeSubheading
      {Web Developer}{Jan. 2024 - Apr. 2024}
      {Northeastern's Young Entrepreneurs}{London, UK}
      \resumeItemListStart
        \resumeItem{Increased website traffic by 50\% through SEO optimization and responsive design implementation on club website.}
        \resumeItem{Integrated SquareSpace API for ticketing, resulted in a 30\% increase in online event registrations.}
        \resumeItem{Collaborated with team to resolve technical challenges, improved site performance and streamlined user experience.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd



   






%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
             \resumeProjectHeading
          {\textbf{GraduateNU} $|$ \emph{Sandbox}}{Sep. 2024 - Present}
          \resumeItemListStart
            \resumeItem{Developing solution for a sandbox area to allow students to experiment with placeholder courses.}
            \resumeItem{Prioritized on debugging React frontend and adding new features to an existing codebase of over 40k files.}
            \resumeItem{Implemented a cross-project API function to fetch information about individual courses in a degree audit plan.}
        
          \resumeItemListEnd
          
     \resumeProjectHeading
          {\textbf{teXnology} $|$ \emph{Berkeley AI Hackathon 2024}}{Jun. 2024}
          \resumeItemListStart
            \resumeItem{Led team of 3 developers in the Berkeley AI Hackathon to build a fullstack web application to format speech to LaTeX}
            \resumeItem{Integrated Groq’s chat completion model and Openleaf API to enhance user experience and accessibility}
            \resumeItem{Presented project in front of multiple rounds of judging in the Berkeley ASUC Student Union building.}
            \resumeItem{Leveraged a speech recognition libary on NPM to convert speech to text with over 90\% accuracy on demo day.}
          \resumeItemListEnd

     \resumeProjectHeading
          {\textbf{EquilibriNews} $|$ \emph{Nextjs, JavaScript, React, Playwright}}{Apr. 2022 -  Jan. 2024}
          \resumeItemListStart
            \resumeItem{Developed a website to scrape news from major publishers and displayed in a way that reduced political bias}
            \resumeItem{Implemented Google's Puppeteer API and Playwright to scrape data from news websites including New York Times, Fox News, Wall Street Journal, etc.}
            \resumeItem{Consulted UPenn Master's Graduate Melissa Amaya through the Polygence platform for technical advice}
          \resumeItemListEnd
        
          \resumeItemListEnd 
          

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Front end}{: React, Nextjs, Figma, Canva, Adobe Illustrator, Tailwind CSS, Chakra-UI, Bootstrap} \\
     \textbf{Back end}{: Java, Python, Kotlin, JavaScript, TypeScript, Nodejs, Express, NestJs, PostgreSQL, Firebase, MongoDB} \\
     \textbf{Developer Tools}{: Git, Docker, npm, Eclipse, Vercel, Netlify, Google Cloud Platform, Amazon Web Services} \\
     \textbf{Data Science + Visualization}{: pandas, NumPy, MATLAB, Tableau, Puppeteer, streamlit, matplotlib, Mage}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
