%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
     
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\eduSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5}
     
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Yicheng (Dennis) Wang} \\ \vspace{1pt}
    \small 949-375-1978 $|$ \href{mailto:denniswang812@gmail.com}{\underline{denniswang812@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/denniswang812/}{\underline{LinkedIn}} $|$
    \href{https://github.com/hellolol2016}{\underline{GitHub}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \eduSubheading
      {Northeastern University}{Boston, MA}
      {Bachelor of Science in Computer Science + Business Administration, GPA: 3.78}{Sept. 2023 -- June 2027}
        {Relevant Courses: Discrete Structures - A, Fundamentals of CS 1+2 - A, Financial Accounting - A}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------

      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Software Developer}{Sep. 2024 - Present}
      {Sandbox}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Part of the development team on GraduateNU, participated in Agile sprints over a semester long period}
        \resumeItem{Exercised soft skills like time managment and effective communication by balancing club activities and school.}
        \resumeItem{Contributed to a multi-semester project that impacts the lives of over 23,000 undergraduate students}
    \resumeItemListEnd

       \resumeSubheading
      {Developer}{Sep. 2024 - Present}
      {Code 4 Community}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Working part-time for a community-focused software consultancy at Northeastern University. }
        \resumeItem{Participated in weekly meetings and actively contributing to Securing Safe Food, a platform to onboard pantries, receive food requests, keep track of deliveries, etc. in one comprehensive portal.}
    \resumeItemListEnd

   \resumeSubheading
      {Mentor}{Sep. 2024 - Present}
      {Oasis}{Northeastern University, Boston, MA}
      \resumeItemListStart
        \resumeItem{Partook in project ideation workshops. Helped club members brainstorm their ideas}
        \resumeItem{Mentoring groups of new developers on a weekly basis to develop a tangible application by the end of the semester.}
    \resumeItemListEnd
  
 \resumeSubheading
      {Web Developer}{Jan. 2024 - Apr. 2024}
      {Northeastern's Young Entrepreneurs}{London, UK}
      \resumeItemListStart
        \resumeItem{Enhanced Entrepreneur Club's SquareSpace site with custom features using previous web dev skills.}
        \resumeItem{Integrated ticketing API to streamline event management and boost user engagement.}
        \resumeItem{Collaborated with team to resolve technical challenges, improving site performance and user experience.}
    \resumeItemListEnd

     \resumeSubheading
      {Private Tennis Instructor}{May 2023 - Aug. 2024}
      {Self employed}{Orange County, CA}
      \resumeItemListStart
        \resumeItem{Provided personalized tennis coaching to 10+ students, ages ranging from 9 - 20+, helping each achieve significant improvements in technique and performance.}
        \resumeItem{Designed and implemented customized training programs for various age groups, focusing on skill development, physical fitness, and strategic gameplay.}
        \resumeItem{Effectively communicated with students and parents to set goals, provide feedback, and ensure a supportive learning environment.}
    \resumeItemListEnd

     \resumeSubheading
      {Tennis Coordinator / Coach}{Nov. 2021 - Sep. 2023}
      {Veylix Tennis Academy}{Orange County, CA}
      \resumeItemListStart
        \resumeItem{Managed daily training schedules for a team of 20+ students.}
        \resumeItem{Organized and supervised academy games, enhancing competitive experience and fostering a sense of community.}
        \resumeItem{Coorindated Coach allocation for summer camps using Google Sheets, ensuring all sessions were properly staffed.}
    \resumeItemListEnd

    \resumeSubheading
      {Engineer \& Research Fellow}{July 2022}
      {University of California, Irvine}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Utilized C++ skills to code an Arduino board; developed a MATLAB script taking input from an IMU for a hands-free mouse for individuals with disabilities.}
        \resumeItem{Used the Fusion 360 software to design a user-friendly and ergonomic device for 3D printing}
        \resumeItem{Conducted a live demonstration of the product to UCI professors and fellow research peers}
         \resumeItem{Awarded the Certificate of Research \& Innovation Leadership for completing the BEAM program requirements, demonstrating outstanding research, innovation, and entrepreneurship skills.}
      \resumeItemListEnd

    \resumeSubheading
      {Programmer \& Builder}{June 2021 --  May 2022}
      {VEX Robotics}{Irvine, CA}
      \resumeItemListStart
        \resumeItem{Played a pivotal role as a programmer and builder for VEX team 2496R, contributing to our performance at the VEX Worlds competition.}
        \resumeItem{Optimized a critical robot autonomous turn function to under 20 lines in an established codebase via Git}
        \resumeItem{Volunteered at school district hosted events, leveraging robotics expertise to engage and inspire the community while giving back through knowledge sharing and mentorship}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



   






%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
         \resumeProjectHeading
          {\textbf{GraduateNU} $|$ \emph{Sandbox Fall 2024}}{Sep. 2024 -- present}
          \resumeItemListStart
            \resumeItem{Worked in an agile development workflow to contribute to a degree audit application used by undergraduate students}
            \resumeItem{Prioritized on debugging and adding new features to an existing codebase of over 40k files.}
          \resumeItemListEnd
         
         \resumeProjectHeading
          {\textbf{teXnology} $|$ \emph{Berkeley AI Hackathon 2024}}{Jun. 2024}
          \resumeItemListStart
            \resumeItem{Led team of 3 developers in the Berkeley AI Hackathon to build a fullstack web application to format speech to LaTeX}
            \resumeItem{Integrated Groq’s chat completion model and Openleaf API to enhance user experience and accessibility}
            \resumeItem{Presented project in front of multiple rounds of judging, in the Berkeley ASUC Student Union building.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{EquilibriNews} $|$ \emph{Nextjs, JavaScript, React, Playwright}}{Feb. 2022 --  March 2023}
          \resumeItemListStart
            \resumeItem{Developed a website to scrape news from major publishers and displayed in a way that reduced political bias}
            \resumeItem{Implemented Google's Puppeteer API and Playwright to scrape data from news websites}
            \resumeItem{Consulted UPenn Master's Graduate Melissa Amaya through the Polygence platform for technical advice}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{WanderWorks} $|$ \emph{Figma, Canva, Adobe Premiere Pro}}{May 2024}
          \resumeItemListStart
            \resumeItem{Designed and prototyped an IOS application using Figma's design and wireframe tools}
            \resumeItem{Developed a subscription-based business model and presented it to an audience of over 100 participants in Donald Bren Hall }
            \resumeItem{Completed project along with video demo within a strict 36 hour timeline}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{ImpaKt} $|$ \emph{Figma, Tome}}{March 2024}
          \resumeItemListStart
            \resumeItem{Prototyped and designed a crowdfunding application for Hack The Globe 2024}
            \resumeItem{Implemented dual investment options, allowing investors to choose between passive and active investment strategies, thereby increasing user engagement and flexibility.}
            \resumeItem{Pitched idea to senior BCG consultants at the BCG London Office}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{IM33 - Diagnosis of Autism Spectrum Disorder} $|$ \emph{Python, Tensorflow, IBM Z Mainframe Platform}}{Oct. 2023}
          \resumeItemListStart
            \resumeItem{Led and managed a cross-functional team of 6 members in a 24-hour datathon}
            \resumeItem{Developed a machine learning model that uses TensorFlow to analyze eye-tracking data from videos to predict for autism in young children}
            \resumeItem{Achieved a score of over 60 accuracy for the model analyzing a dataset of footage of eye movements}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Uber Data Dashboard} $|$ \emph{Python, Google Cloud Platform, BigQuery, Mage, Looker Studio}}{July 2023}
          \resumeItemListStart
            \resumeItem{Leveraged Python for data preprocessing, transformation, and formatting, ensuring data quality for subsequent analysis}
            \resumeItem{Used Google Cloud Storage to host files, Google Compute Engine and Mage as data pipeline to the Cloud}
            \resumeItem{Utilized Google BigQuery for data processing, and Google Looker Studio to create a dashboard}
          \resumeItemListEnd

           \resumeProjectHeading
          {\textbf{CultureCanvas} $|$ \emph{NextJs, JavaScript, REST APIs, Nodejs}}{June 2023}
          \resumeItemListStart
            \resumeItem{Developed a full stack Next.js application utilizing the Art Institute of Chicago API, featuring over 100,000 art pieces}
            \resumeItem{Leverages NextJs' serverless functions to remove need to host separate server, reducing cost}
            \resumeItem{Incorporated gamification techniques, such as quizzes for different cultures and art forms}

          \resumeItemListEnd 
          
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Front-end}{: HTML/CSS, React, Nextjs, Figma, Canva, Adobe Illustrator, Tailwind CSS, Material-UI, Bootstrap} \\
     \textbf{Back-end}{: Java, Python, Kotlin, JavaScript, TypeScript, Nodejs, Express, PostgreSQL, Firebase, MongoDB} \\
     \textbf{Developer Tools}{: Git, VS Code, npm, Docker, Vercel, Netlify, Google Cloud Platform, Amazon Web Services} \\
     \textbf{Data Science + Visualization}{: pandas, NumPy, MATLAB, Tableau, Puppeteer, streamlit, matplotlib, Mage}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
